\vspace{-3em} \includegraphics[width=.1\textwidth]{Figures/logo.png} \\ \includegraphics[width=4cm]{Figures/logotext.png} \\

### 2014-10-20 report/article_4.tex
new report figure; cut-down

A full report with additional visualisations is online at {\bf
  \leavevmode\href{http://blm.io/datarea}{blm.io/datarea} }and scripts to
reproduce all analyses are available from {\bf
  \leavevmode\href{http://github.com/blmoore/summerdatachallenge}{github.com/blmoore/summerdatachallenge}}.

@@

\subsection*{Fractal context}

@@

\subsection*{ARIMA modelling}

@@

\vspace{-1em}
\subsection*{Investment grading}

@@

As an example, Figure 3 shows the top 5 best-ranked postcode sectors
in which to invest, according to their 12-month price growth forecast
and historical annualised volatility --- thus combining the empirical
data with theoretical model outputs. These include South London
suburbs of Upper Tooting and Morden, as well as Walthamstow in East
London, and Brockley,
whose train station within SE4 1 was linked with the London Overground network in 2010.\\

@@

The rankings used in Figure 3 made use of the $drift$ parameter of
ARIMA models, combined with statistical volatility over the five year
house prices dataset. Both parameters were converted to quantiles and
weighted equally; those sectors with the highest projected growth
and least historical volatility receive the highest investment grade
(on a scale of AAA, AA, A, BBB \ldots C).\textsuperscript{$\star$}

Returning to our original example, we can conclude that SW18 4HU is a
promising choice of area for property investment. It's approximately
median-priced for the sector, which is the cheapest of SW18 (in turn
part of the desirable SW London area; Figure 1). It has good growth
projections of XX in the next 12 months (Figure 2), and when combined
with volatility and compared with all $\approx2600$ sectors in the
dataset, receives the top AAA investment grade, placing it in the
90\textsuperscript{th} percentile for predicted price growth and low
historical volatility.

>>>>

A full report with additional interactive visualisations is online at {\bf
  \leavevmode\href{http://blm.io/datarea}{blm.io/datarea} }and scripts to
reproduce all analyses are available from {\bf
  \leavevmode\href{http://github.com/blmoore/summerdatachallenge}{github.com/blmoore/summerdatachallenge}}.

@@

\vspace{-.5em}
\subsection*{Fractal context}

@@

\vspace{-.5em}
\subsection*{ARIMA modelling}

@@

\vspace{-2em}
\subsection*{Investment grading}

@@

As an example, Figure 3 shows the top 5 postcode sectors
in which to invest, according to their 12-month price growth forecast
and historical annualised volatility --- thus combining the empirical
data with theoretical model outputs. These include Brockley,
whose train station within SE4 1 was linked with the London Overground network in 2010.\\

@@

\setlength{\intextsep}{0em}
\begin{wrapfigure}{R}{.45\textwidth}
%\vspace{-1em}
\centering
\includegraphics[width=.44\textwidth]{Figures/grading.png}
\vspace{-1em}
\caption{ Quantile transformation for investment grading
  (AAA rated sectors in \emph{navy}).}
\vspace{.5em}
\end{wrapfigure}

Growth forecasts and volatility were converted to quantiles and
weighted equally; those sectors with the highest projected growth
and least historical volatility receive the best investment grade
(on a scale of AAA, AA, A, BBB \ldots C).\textsuperscript{$\star$}

Returning to our original example, SW18 4HU is a promising choice of
area for property investment. It's median-priced for the sector, which
is the cheapest of SW18 (in turn part of the desirable SW London area;
Figure 1). It has good growth projections of over £28,000 in the next
year (Figure 2), and receives the top AAA investment grade, being
in the 90\textsuperscript{th} percentile for predicted price growth
and low historical volatility in the dataset.
